Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-11-25 paper/paper-mainfile.tex
Added (partial) literal comparision, re-arranged tables, proof incl. poss eff, removed guaranteed effects definition

\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
\newcommand{\PossEffPlus} {\ensuremath{\mathit{poss-eff^{+}_{*}}}}
\newcommand{\PossEffMinus} {\ensuremath{\mathit{poss-eff^{-}_{*}}}}

\newcommand{\RelEffPlus} {\ensuremath{\mathit{eff^{\emptyset +}_{*}}}}
\newcommand{\RelEffMinus} {\ensuremath{\mathit{eff^{\emptyset -}_{*}}}}
\newcommand{\RelPossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset +}_{*}}}}
\newcommand{\RelPossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset -}_{*}}}}

@@

\section{Inference of Preconditions and Effects}
The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks. We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other.

@@

\emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement. So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
if $E(c) \neq \emptyset$ and $prec(c) := undef$ otherwise.

State-independent positive and negative effects (cf. their
Def. 4) of a compound task c are facts that are added or
deleted, resp., by the successful execution of a refinement of
c, independent of the state in which the task is executed, i.e.
$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$

Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
after every refinement of c but after at least one:
$$ \RelPossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
$$ \RelPossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
if $E(c) \neq \emptyset$ and $prec(c) := undef$ otherwise.

@@

So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
Then, the precondition-relaxed effects $\RelEffPlus$, $\RelEffMinus$, $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.

There exists a polynomial-time algorithm for inferring the precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
In this paper, we will be utilizing the precondition-relaxed possible effects, which guaranteed to hold after at least one refinement of c.

@@

\subsection{Theoretical Properties If Using Simple Inference (for Grounded Or Lifted)}
\begin{theorem}\label{thm:Soundness}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
	then the solution set of $P'$, denoted $sol(P')$ is a strict subset of $sol(P)$.
\end{theorem}
\begin{proof}
	The new desired orderings for a method include all of the orderings already required by the method originally. The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph. This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one. Any solution to the linearized problem is then obviously a solution to the original problem.
\end{proof}

@@

\begin{description}
	\item[Linearization Criteria] If the linearization process does not find a desired ordering contradicting the existing ones for some method, that method is said to meet the linearization criteria.
	If all methods in a problem meet the linearization criteria, then the problem meets the linearization criteria as well. 
\end{description}
We will now see that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} this criterion is met.

@@

We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20} configured to use to turn the problem into a classical planning problem (in RC model), and Greedy best first search with visited lists. We try this search with 4 different heuristics: FF by \cite{FF}, Add by \cite{Add}, Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem. The same setting is used for re-runs. We also test the latest version of TOHTN planners HTN2SAS, HyperTensioN and Lilotane on the transformed problems. Re-runs use panda$_{\pi}$ with the best heuristic(Add). 
We test both Complex and Simple Inference for linearization. %The comparison is done for grounded linearization variant and the lifted linearization variant 1.

\begin{table*}[h]
	\centering
	\subcaption{Coverage achieved, using Simple Inference on Grounded (Linearized) Problem}
	\scalebox{1} {
	\begin{tabular}{lccccccccccccccccl} 
	\toprule 
	&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} \\ 
	\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}  
	& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
	\midrule 
	Barman-BDI & 20 & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 2.0 &\multicolumn{2}{c}{ \textbf{9.0}  } \\ 
	Monroe Fully Observ.$^{2}$ & 25 & \textbf{25.0} & \textbf{25.0} & 18.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & 15.0 &\multicolumn{2}{c}{ \textbf{16.0}  } \\ 
	Monroe Part. Observ.$^{2}$ & 24 & \textbf{14.0} & \textbf{14.0} & \textbf{7.0} & \textbf{7.0} & 14.0 & \textbf{15.0} & \textbf{10.0} &\multicolumn{2}{c}{ \textbf{10.0}  } \\ 
	PCP$^{17}$ & 17 & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} &\multicolumn{2}{c}{ \textbf{14.0}  } \\ 
	Rover & 20 & 6.0 & \textbf{20.0} & 4.0 & \textbf{14.0} & 4.0 & \textbf{19.0} & 4.0 &\multicolumn{2}{c}{ \textbf{14.0}  } \\ 
	Satellite & 25 & 24.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 24.0 &\multicolumn{2}{c}{ \textbf{25.0}  } \\  
	Transport & 40 & 12.0 & \textbf{28.0} & \textbf{2.0} & \textbf{2.0} & 13.0 & \textbf{14.0} & 7.0 &\multicolumn{2}{c}{ \textbf{12.0}  } \\ 
	UM-Translog$^{1}$ & 22 & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} &\multicolumn{2}{c}{ \textbf{22.0}  } \\ 
	Woodworking$^{2}$ & 30 & 13.0 & \textbf{19.0} & 7.0 & \textbf{15.0} & 12.0 & \textbf{20.0} & 9.0 &\multicolumn{2}{c}{ \textbf{15.0}  } \\ 
	\midrule 
	Monroe & 100 & 96.0 & \textbf{100.0} & 79.0 & \textbf{88.0} & 92.0 & \textbf{100.0} & 81.0 &\multicolumn{2}{c}{ \textbf{90.0}  } \\ 
	SmartPhone$^{1}$ & 7 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
	Zenotravel & 5 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
	\midrule 
	Coverage & 335 & 239.0 & \textbf{287.0} & 188.0 & \textbf{232.0} & 231.0 & \textbf{274.0} & 198.0 &\multicolumn{2}{c}{ \textbf{237.0}  } \\ 
	Norm. coverage & 12 & 8.22 & \textbf{9.95} & 6.85 & \textbf{8.46} & 8.0 & \textbf{9.63} & 7.1 &\multicolumn{2}{c}{ \textbf{8.44}  } \\ 
	\bottomrule 
	\end{tabular}
	}
\end{table*}

@@

\begin{table*}[h]
	\centering
	\caption{IPC score achieved, using Simple Inference, on Grounded Problems}
	\scalebox{1} {
\begin{tabular}{lccccccccccccccccl} 
	\toprule 
	&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} \\ 
	\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}  
	& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
	\midrule 
	Barman-BDI & 1 & 0.08 & \textbf{0.4} & 0.07 & \textbf{0.34} & 0.07 & \textbf{0.36} & 0.05 &\multicolumn{2}{c}{ \textbf{0.22}  } \\ 
	Monroe Fully Observ.$^{2}$ & 1 & \textbf{0.56} & 0.45 & \textbf{0.31} & 0.3 & \textbf{0.46} & 0.41 & \textbf{0.22} &\multicolumn{2}{c}{ 0.18  } \\ 
	Monroe Part. Observ.$^{2}$ & 1 & \textbf{0.31} & 0.25 & \textbf{0.13} & 0.11 & \textbf{0.31} & 0.26 & \textbf{0.17} &\multicolumn{2}{c}{ 0.14  } \\ 
	PCP$^{17}$ & 1 & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} &\multicolumn{2}{c}{ \textbf{0.82}  } \\ 
	Rover & 1 & 0.29 & \textbf{0.95} & 0.14 & \textbf{0.52} & 0.2 & \textbf{0.78} & 0.16 &\multicolumn{2}{c}{ \textbf{0.48}  } \\ 
	Satellite & 1 & 0.91 & \textbf{1.0} & 0.76 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.89 &\multicolumn{2}{c}{ \textbf{0.99}  } \\ 
	Transport & 1 & 0.24 & \textbf{0.61} & 0.04 & \textbf{0.05} & 0.27 & \textbf{0.32} & 0.12 &\multicolumn{2}{c}{ \textbf{0.2}  } \\ 
	UM-Translog$^{1}$ & 1 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
	Woodworking$^{2}$ & 1 & 0.38 & \textbf{0.58} & 0.2 & \textbf{0.41} & 0.36 & \textbf{0.57} & 0.27 &\multicolumn{2}{c}{ \textbf{0.39}  } \\ 
	\midrule 
	Monroe & 1 & \textbf{0.77} & 0.69 & \textbf{0.5} & 0.47 & \textbf{0.75} & 0.71 & \textbf{0.53} &\multicolumn{2}{c}{ \textbf{0.53}  } \\ 
	SmartPhone$^{1}$ & 1 & \textbf{0.71} & \textbf{0.71} & 0.69 & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} &\multicolumn{2}{c}{ \textbf{0.71}  } \\ 
	Zenotravel & 1 & \textbf{1.0} & \textbf{1.0} & 0.63 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.83 &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
	\midrule 
	IPC score & 12 & 7.1 & \textbf{8.4} & 5.3 & \textbf{6.7} & 7.0 & \textbf{7.9} & 5.8 &\multicolumn{2}{c}{ \textbf{6.7}  } \\
	\bottomrule 
\end{tabular} 
	}
\end{table*}

\begin{table*}[h]
	\centering
	\caption{Coverage achieved, using Simple Inference, Lifted Problems}
\begin{tabular}{lccccccccccccccccccl} 
	\toprule 
	&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{Lilotane}\\ 
	\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  
	& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
	\midrule 
	Barman-BDI & 20 & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 2.0 & \textbf{9.0} &\multicolumn{2}{c}{ \textbf{17.0}  } \\ 
	Monroe Fully Observ.$^{7,7,7,5,0}$ & 25 & \textbf{25.0} & \textbf{25.0} & 18.0 & \textbf{22.0} & 22.0 & \textbf{23.0} & \textbf{15.0} & \textbf{15.0} &\multicolumn{2}{c}{ 18.0  } \\ 
	Monroe Part. Observ.$^{2,2,2,2,0}$ & 24 & \textbf{14.0} & 13.0 & \textbf{7.0} & 6.0 & \textbf{14.0} & 13.0 & \textbf{11.0} & 9.0 &\multicolumn{2}{c}{ \textbf{20.0}  } \\ 
	PCP$^{18,18,17,17}$ & 18 & \textbf{15.0} & \textbf{15.0} & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} &\multicolumn{2}{c}{ 0.0  } \\ 
	Rover & 20 & 6.0 & \textbf{15.0} & 4.0 & \textbf{13.0} & 4.0 & \textbf{14.0} & 4.0 & \textbf{13.0} &\multicolumn{2}{c}{ \textbf{20.0}  } \\ 
	Satellite & 25 & 24.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 24.0 & \textbf{25.0} &\multicolumn{2}{c}{ \textbf{25.0}  } \\ 
	Transport & 40 & 12.0 & \textbf{27.0} & \textbf{2.0} & \textbf{2.0} & 13.0 & \textbf{14.0} & 7.0 & \textbf{12.0} &\multicolumn{2}{c}{ \textbf{35.0}  } \\ 
	UM-Translog$^{1,1,1,1,0}$ & 22 & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} &\multicolumn{2}{c}{ 21.0  } \\ 
	Woodworking & 30 & \textbf{13.0} & 7.0 & \textbf{8.0} & 7.0 & \textbf{12.0} & 7.0 & \textbf{9.0} & 7.0 &\multicolumn{2}{c}{ 6.0  } \\ 
	\midrule 
	Monroe & 100 & \textbf{96.0} & 92.0 & 79.0 & \textbf{87.0} & \textbf{92.0} & 90.0 & 81.0 & \textbf{89.0} &\multicolumn{2}{c}{ \textbf{100.0}  } \\ 
	SmartPhone$^{3,3,3,3,0}$ & 7 & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 5.0 & \textbf{6.0} & 5.0 & \textbf{6.0} &\multicolumn{2}{c}{ 1.0  } \\ 
	Zenotravel & 5 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
	\midrule 
	Coverage & 336 & 240.0 & \textbf{263.0} & 190.0 & \textbf{220.0} & 231.0 & \textbf{243.0} & 199.0 & \textbf{226.0} &\multicolumn{2}{c}{ \textbf{268.0}  } \\ 
	Norm. coverage & 12 & 8.23 & \textbf{9.45} & 6.9 & \textbf{8.12} & 8.0 & \textbf{8.83} & 7.14 & \textbf{8.18} &\multicolumn{2}{c}{ 8.58  } \\ 
	\bottomrule 
\end{tabular} 
\end{table*}

>>>>

%\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
%\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
\newcommand{\PossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{+}_{*}}}}
\newcommand{\PossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{-}_{*}}}}

%\newcommand{\RelEffPlus} {\ensuremath{\mathit{\textit{eff}^{\emptyset +}_{*}}}}
%\newcommand{\RelEffMinus} {\ensuremath{\mathit{\textit{eff}^{\emptyset -}_{*}}}}
\newcommand{\RelPossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset +}_{*}}}}
\newcommand{\RelPossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset -}_{*}}}}

@@

\section{Inference of Preconditions and Effects}
The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks. We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other. This random removal of contradicting orderings is called \textbf{\textit{cycle-breaking}}.

@@

\emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement. So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.

%State-independent positive and negative effects (cf. their Def. 4) of a compound task c are facts that are added or deleted, resp., by the successful execution of a refinement of c, independent of the state in which the task is executed, i.e.
%$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
%$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$

Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
after every refinement of c but after at least one:
$$ \PossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
$$ \PossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
if $E(c) \neq \emptyset$ and  $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.

@@

So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.

Then, the precondition-relaxed effects $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
This means $\RelPossEffPlus$ and $\RelPossEffMinus$ has every effect that $\PossEffPlus$ and $\PossEffMinus$  do, respectively. But
the precondition relaxation can make further refinements executable that produce
effects that can not be achieved in the non-relaxed domain. 
In other words, we can calculate a super-set, that might contain some false candidates, of the real preconditions and effects that might occur after any execution of $c$, i.e.\  $\PossEffMinus \subseteq \RelPossEffMinus$, and $\PossEffPlus  \subseteq \RelPossEffPlus$.

There exists a polynomial-time algorithm for inferring the mandatory preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
In this paper, we will be utilising both of these, as seen in the next section.
%the precondition-relaxed possible effects, which may hold after at least one refinement of c.

@@

\begin{theorem}\label{thm:Soundness}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
	then the solution set of $P'$, denoted $sol(P')$ is a strict subset of $sol(P)$.
\end{theorem}
\begin{proof}
	The new desired orderings for a method include all of the orderings already required by the method originally. The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph. This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one. Any solution to the linearized problem is then obviously a solution to the original problem.
\end{proof}

@@

% The exploitation of the relaxed preconditions and effects
% is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates.

\begin{description}
	\item[Linearization Criteria] If the linearization process does not find any desired ordering contradicting the existing ones for some method, (i.e.\ nothing needs to be removed when cycle-breaking) that method is said to meet the linearization criteria.
	If all methods in a problem meet the linearization criteria, then the problem meets the linearization criteria as well. 
\end{description}

We will now prove that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} uses simple inference or preconditions and possible effects from complex inference, and this criterion is met.

%\textit{Note that this criteria does not apply if using preconditions and guaranteed effects from complex inference}, as those are a \emph{subset} of possible preconditions and effects -- and thus there may be other, unknown effects that impact the executability of the sequence produced by Algorithm~\ref{alg:Algorithm1}.

%Specifically, unknown mandatory delete effects may render the chose linearization un-executable. Otherwise, it is notable that mandatory effects all occur in the state.

%On the other hand possible preconditions and effects - if they never occur, that's also a problem the PO version has to deal with.

@@

We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20} configured to use to turn the problem into a classical planning problem (in RC model), and Greedy best first search with visited lists. We try this search with 4 different heuristics: FF by \cite{FF}, Add by \cite{Add}, Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem. The same setting is used for re-runs. We also test the latest version of TOHTN planners HTN2SAS, HyperTensioN and Lilotane on the transformed problems. Re-runs use panda$_{\pi}$ with the best heuristic(Add). 
We test both Complex and Simple Inference for linearization.

The results table for both coverage and IPC score can be seen on page \pageref{table:GroundedSimpleIPC}--\pageref{table:GroundedComplexIPC}.
As we can see from those figures, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
The planner that has achieved the highest overall coverage and IPC score is ? planner.

%The comparison is done for grounded  linearization variant and the lifted linearization variant 1. # \value{page}

Unfortunately, when using simple inference, there are very few problems for which all partially ordered methods are linearized without conflict.
Fortunately, when using complex inference, most partially ordered methods in all problems are linearized without conflict.
Figure~\ref{fig:ProblemsLinearizedWOCycleBreak} shows the comparison between the two.

@@

\begin{table*}
	\centering
	\caption{Coverage achieved, using Simple Inference on Grounded Problems}
	\label{table:GroundedSimpleCoverage}
	\scalebox{0.8} {
		\begin{tabular}{lccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}  
			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
			\midrule 
			Barman-BDI & 20 & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 2.0 &\multicolumn{2}{c}{ \textbf{9.0}  } \\ 
			Monroe Fully Observ.$^{2}$ & 25 & \textbf{25.0} & \textbf{25.0} & 18.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & 15.0 &\multicolumn{2}{c}{ \textbf{16.0}  } \\ 
			Monroe Part. Observ.$^{2}$ & 24 & \textbf{14.0} & \textbf{14.0} & \textbf{7.0} & \textbf{7.0} & 14.0 & \textbf{15.0} & \textbf{10.0} &\multicolumn{2}{c}{ \textbf{10.0}  } \\ 
			PCP$^{17}$ & 17 & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} &\multicolumn{2}{c}{ \textbf{14.0}  } \\ 
			Rover & 20 & 6.0 & \textbf{20.0} & 4.0 & \textbf{14.0} & 4.0 & \textbf{19.0} & 4.0 &\multicolumn{2}{c}{ \textbf{14.0}  } \\ 
			Satellite & 25 & 24.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 24.0 &\multicolumn{2}{c}{ \textbf{25.0}  } \\  
			Transport & 40 & 12.0 & \textbf{28.0} & \textbf{2.0} & \textbf{2.0} & 13.0 & \textbf{14.0} & 7.0 &\multicolumn{2}{c}{ \textbf{12.0}  } \\ 
			UM-Translog$^{1}$ & 22 & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} &\multicolumn{2}{c}{ \textbf{22.0}  } \\ 
			Woodworking$^{2}$ & 30 & 13.0 & \textbf{19.0} & 7.0 & \textbf{15.0} & 12.0 & \textbf{20.0} & 9.0 &\multicolumn{2}{c}{ \textbf{15.0}  } \\ 
			\midrule 
			Monroe & 100 & 96.0 & \textbf{100.0} & 79.0 & \textbf{88.0} & 92.0 & \textbf{100.0} & 81.0 &\multicolumn{2}{c}{ \textbf{90.0}  } \\ 
			SmartPhone$^{1}$ & 7 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
			Zenotravel & 5 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
			\midrule 
			Coverage & 335 & 239.0 & \textbf{287.0} & 188.0 & \textbf{232.0} & 231.0 & \textbf{274.0} & 198.0 &\multicolumn{2}{c}{ \textbf{237.0}  } \\ 
			Norm. coverage & 12 & 8.22 & \textbf{9.95} & 6.85 & \textbf{8.46} & 8.0 & \textbf{9.63} & 7.1 &\multicolumn{2}{c}{ \textbf{8.44}  } \\ 
			\bottomrule 
		\end{tabular}
	}
\end{table*}

\begin{table*}
	\centering
	\caption{IPC score achieved, using Simple Inference on Grounded Problems}
	\label{table:GroundedSimpleIPC}
	\scalebox{0.85} {
		\begin{tabular}{lccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}  
			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
			\midrule 
			Barman-BDI & 1 & 0.08 & \textbf{0.4} & 0.07 & \textbf{0.34} & 0.07 & \textbf{0.36} & 0.05 &\multicolumn{2}{c}{ \textbf{0.22}  } \\ 
			Monroe Fully Observ.$^{2}$ & 1 & \textbf{0.56} & 0.45 & \textbf{0.31} & 0.3 & \textbf{0.46} & 0.41 & \textbf{0.22} &\multicolumn{2}{c}{ 0.18  } \\ 
			Monroe Part. Observ.$^{2}$ & 1 & \textbf{0.31} & 0.25 & \textbf{0.13} & 0.11 & \textbf{0.31} & 0.26 & \textbf{0.17} &\multicolumn{2}{c}{ 0.14  } \\ 
			PCP$^{17}$ & 1 & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} &\multicolumn{2}{c}{ \textbf{0.82}  } \\ 
			Rover & 1 & 0.29 & \textbf{0.95} & 0.14 & \textbf{0.52} & 0.2 & \textbf{0.78} & 0.16 &\multicolumn{2}{c}{ \textbf{0.48}  } \\ 
			Satellite & 1 & 0.91 & \textbf{1.0} & 0.76 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.89 &\multicolumn{2}{c}{ \textbf{0.99}  } \\ 
			Transport & 1 & 0.24 & \textbf{0.61} & 0.04 & \textbf{0.05} & 0.27 & \textbf{0.32} & 0.12 &\multicolumn{2}{c}{ \textbf{0.2}  } \\ 
			UM-Translog$^{1}$ & 1 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
			Woodworking$^{2}$ & 1 & 0.38 & \textbf{0.58} & 0.2 & \textbf{0.41} & 0.36 & \textbf{0.57} & 0.27 &\multicolumn{2}{c}{ \textbf{0.39}  } \\ 
			\midrule 
			Monroe & 1 & \textbf{0.77} & 0.69 & \textbf{0.5} & 0.47 & \textbf{0.75} & 0.71 & \textbf{0.53} &\multicolumn{2}{c}{ \textbf{0.53}  } \\ 
			SmartPhone$^{1}$ & 1 & \textbf{0.71} & \textbf{0.71} & 0.69 & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} &\multicolumn{2}{c}{ \textbf{0.71}  } \\ 
			Zenotravel & 1 & \textbf{1.0} & \textbf{1.0} & 0.63 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.83 &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
			\midrule 
			IPC score & 12 & 7.1 & \textbf{8.4} & 5.3 & \textbf{6.7} & 7.0 & \textbf{7.9} & 5.8 &\multicolumn{2}{c}{ \textbf{6.7}  } \\
			\bottomrule 
		\end{tabular} 
	}
\end{table*}
